\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-08-13 tex/gitlinks.tex
contrast integral

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_gp/blob/eb1218eef62c9812177173e82fdc6d095fc1e432/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_gp/blob/eb1218eef62c9812177173e82fdc6d095fc1e432/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_gp/blob/eb1218eef62c9812177173e82fdc6d095fc1e432/#1}{\raisebox{-0.1em}{\prooficon}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_gp/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_gp/blob/770b39c492f27102f9a66dc6061f06370f0306e9/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_gp/blob/770b39c492f27102f9a66dc6061f06370f0306e9/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_gp/blob/770b39c492f27102f9a66dc6061f06370f0306e9/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_gp/_build}{#1}}
